---
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE)
# library(flexdashboard)
try(detach("package:intraday", unload=TRUE),silent = TRUE) # Update: Does not return error message to prevent confusion
library(intraday)
library(lubridate)
library(dplyr)
library(reactable)
library(echarts4r)
```


```{r get_raw_price_data}
price_df_raw <- readr::read_csv(system.file("market-data/price_data.csv",package="intraday"),locale=readr::locale(tz="Turkey"))
colnames(price_df_raw)[1] <- "X1" ## TEMP fix

price_df <- price_df_raw %>% select(-X1) %>% mutate(date=as_datetime(date,tz="Turkey")) %>% relocate(aof,.after=mcp) 

summary_df_raw <- readr::read_csv(system.file("market-data/intraday_summary.csv",package="intraday"),locale=readr::locale(tz="Turkey"))
colnames(summary_df_raw)[1] <- "X1" ## TEMP fix

transactions_df_raw <- readr::read_csv(system.file("market-data/intraday_transactions.csv",package="intraday"),locale=readr::locale(tz="Turkey"))
colnames(transactions_df_raw)[1] <- "X1" ## TEMP fix

tx_df <- preprocess_transactions_df(transactions_df_raw)

the_date <- as_date(names(table(as_date(price_df_raw$date)))[1])

```


---
title: "EPIAS Intraday Market Report of `r format(the_date,format="%b %d, %Y")` (BETA)"
---

<!-- <h1>Report of `r format(the_date,format="%b %d, %Y")`</h1> -->

## Summary

```{r}
valuebox_vec <-  price_df %>% mutate(pd_aof_mcp = aof-mcp,pd_aof_smp = aof-smp) %>% summarise(md_mcp=round(mean(pd_aof_mcp),2),md_smp=round(mean(pd_aof_smp),2)) %>% unlist()

header_df <- 
tibble(name= "Total Intraday Market Volume (TIMV)" ,value=summary_df_raw %>% summarise(timv=round(sum(tradingVolume))) %>% unlist() %>% paste0("TRY ",.)) %>%
  add_row(name="Mean Deviation from MCP",value=paste0("TRY ",valuebox_vec["md_mcp"])) %>%
  add_row(name="Mean Deviation from SMP",value=paste0("TRY ",valuebox_vec["md_smp"])) 

reactable(header_df,striped = TRUE)
```


<div class="alert alert-warning role="alert" style="width:99%; height:100%;"> 
<h2> Today's startup! </h2>
<p>Project Intraday has an objective to promote a startup or organization each day. You can <a href="https://www.linkedin.com/in/berkorbay/" target="_blank">contact me on Linkedin</a> if you want to be featured.</p>

<p> <strong>Açık Enerji</strong> (Open Energy) is a Github organization of repositories and external links about data analysis in energy sector. Repositories and links also contain code and data as well as the analyses.</p>

<p><a href="https://github.com/acikenerji" target="_blank">Click here to learn more</a></p>
</div>

## Daily Chart and Data

```{r price_formation_chart}
price_df %>% mutate(hour = hour(date)) %>% select(-smpDirection,-date) %>% rename(MCP=mcp,WAP=aof,SMP=smp) %>% tidyr::pivot_longer(-hour) %>% group_by(name) %>% e_chart(hour)  %>% e_line(value) %>% e_title("Price Chart") %>% e_tooltip(trigger = "axis") # tooltip
```

```{r price_table, eval=FALSE}
price_table_df <- price_df %>% arrange(date) %>% transmute(Hour = format(date,"%b %d, %Y %H:%M"),MCP=mcp,WAP=aof,SMP=smp,`SMP Direction`=smpDirection)

reactable(price_table_df,defaultPageSize = 24,height = 350,
  striped = TRUE)
```

## Contract Distribution

```{r}
tx_df %>% group_by(contract) %>% summarise(total_mwh = sum(quantity_in_mwh*pmax(1,block_hours))) %>% ungroup() %>% arrange(desc(total_mwh)) %>% slice(1:20) %>% arrange(total_mwh) %>% e_chart(contract,reorder = FALSE) %>% e_bar(total_mwh,reorder = FALSE) %>%  e_legend(FALSE) %>% e_title("Top 20 Contracts by Total Volume in MWh")  %>%  e_y_axis(splitLine = list(show = FALSE), axisLabel = list(
    interval = 0L
  )) %>% e_flip_coords() %>% e_x_axis(show = FALSE) %>% e_labels(position = "right")

```


# About the report

- This is a free report and authors do not admit any responsibility about the report or the data.
- This report is meant to refresh itself each day automatically. Essentially an R package, an external python script and Github Actions make it possible. Blog post to follow soon...
- Data is taken from [EPIAS Seffaflik Platformu](https://seffaflik.epias.com.tr/), data provider of the Turkish Energy Exchange.
- Almost all code is openly shared on its [Github repository](https://github.com/berkorbay/intraday). You may use the code in line with the license (MIT license).
- For improvement, analysis and data requests [contact me on Linkedin](https://www.linkedin.com/in/berkorbay/). For raw data csv files [click here](https://github.com/berkorbay/intraday/tree/prod/inst/market-data).



